ZCB Pricing

### 2018-07-01 ZCB Pricing .Rmd
Added some initial conditions to the explicit funciton. Not sure what this funciton outputs though? Need to know to continue
New explicit example

explicit <- function(alpha, beta, sigma, T, r, j, s){

# j = number of sub-intervals for the short rate
# s = number of sub-intervals for the time interval

dr = 1/j # lenght of short rate intervals
dt = T/s # lenght of time intervals

p_d <- sigma^2/(2*((dr)^2)) -(alpha -beta*r)/(2*dr)
p_m <- 1/dt -(sigma^2)/(dr^2)
p_u <- sigma^2/(2*(dr^2)) +(alpha -beta*r)/(2*dr)

V <- matrix(NA, nrow = j + 1, ncol = s + 1)
V[,s+1] <- rep(1)
V[j+1,] <- rep(1)
for (n in seq(s,0,-1)){
    for (i in 1:j)
       if (i == 1)
         V[i,n] <- ((0.10 +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i+2,n+1]) #Vetzal approx
       else
         V[i,n] <- ((0.11 -0.01*i +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i-1,n+1])

}
V
}

>>>>

alpha = 0.01
beta = 0.1
sigma = 0.04
I = 1:20
J = seq(0,0.2,0.005)

dt = 1/length(I)
dr = J[2] -J[1]

J[8]
nr <- length(J)
nt <- length(I)+1
V <- matrix(NA, nrow = length(J), ncol = length(I)+1)

V[,length(I)+1] <- rep(1)

count <- 0
for (i in rev(I)){
  count <- count+1
for (j in (1+count):(nr-count)){
  pu <- sigma^2/(2*dr^2) + (alpha -beta*J[nr-j])/(2*dr)
  pm <- 1/dt -sigma^2/(dr^2)
  pd <- sigma^2/(2*(dr^2)) - (alpha -beta*J[nr-j])/(2*dr) 
  V[j,i] <- (1/(J[nr-j]+1/dt))*(pu*V[j-1,i+1] + pm*V[j,i+1] +pd*V[j+1,i+1])
}

}

V[(nr+1)/2,1]
